OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-15 paper/paper.Rmd
Concluding discussion paragraph

When fitting with the split dataset strategy, OTU quality was remarkably similar
when reference sequences were selected by a simple random sample or weighted by
abundance, but quality was slightly worse when sequences were weighted by
similarity. 
We recommend using a simple random sample since the more
sophisticated reference selection methods do not offer any benefit. 
The similarity in OTU quality between OptiClust and OptiFit with this strategy
demonstrates the suitability of using OptiFit to fit sequences to existing OTUs,
such as when using already-trained machine learning models to make predictions
on new data or comparing OTUs across studies.
However, when stable OTUs are not required, we recommend using OptiClust for _de
novo_ clustering over the split strategy with OptiFit since OptiClust is simpler
to execute but performs similarly in terms of both run time and OTU quality.

**TODO: big picture concluding paragraph.**
We have developed a new clustering algorithm that allows users to produce high
quality OTUs using already existing OTUs as a reference.
**TODO: Point to courtney's paper metaphorically. wow what a cool application someone should do _wink wink_.**

>>>>

When fitting with the split dataset strategy, OTU quality was remarkably similar
when reference sequences were selected by a simple random sample or weighted by
abundance, but quality was slightly worse when sequences were weighted by
similarity. 
We recommend using a simple random sample since the more
sophisticated reference selection methods do not offer any benefit. 
The similarity in OTU quality between OptiClust and OptiFit with this strategy
demonstrates the suitability of using OptiFit to fit sequences to existing OTUs,
such as when comparing OTUs across studies.
However, when stable OTUs are not required, we recommend using OptiClust for _de
novo_ clustering over the split strategy with OptiFit since OptiClust is simpler
to execute but performs similarly in terms of both run time and OTU quality.

We have developed a new clustering algorithm that allows users to produce high
quality OTUs using already existing OTUs as a reference.
Unlike existing reference-based methods which map query sequences to a single
centroid sequence in each reference OTU, OptiFit considers all sequences in each
reference OTU when fitting query sequences, resulting in OTUs of a similar high
quality as those produced by the _de novo_ OptiClust algorithm.
Potential applications include fitting sequences to reference databases,
comparing taxonomic composition of microbiomes across different studies, 
or using OTU-based machine learning models to make predictions on new data.
OptiFit fills the missing option for fitting query sequences to existing OTUs
that does not sacrifice OTU quality for stability of OTU assignments.
